### 2020-09-22 latex/vlp.tex
Updated intro to VLP chapter

The motion of the VLP has been well studied (see for instance
\cite{dynamics_periodic_vlp}), and many control mechanisms exist
to stabilize trajectories of the system. While many of these controllers 
are time-dependent, \citet{vlp_energy_shaping}
offer a time-independent technique to inject energy into the system. 
They designed a controller through a technique called \textit{energy
shaping}, and proved that their control mechanism would allow the VLP to achieve
any desired energy level set.
However, the energy injection mechanism is ad-hoc in the sense that it is not
derived from natural behaviour. 
In this chapter we will design VNHCs to inject energy into the VLP in a
time-independent way.
The difference compared to \cite{vlp_energy_shaping} is that our 
controller will maintain the structured motion of a human on a swing.

>>>>

The motion of the VLP has been well studied (see for instance
\cite{dynamics_periodic_vlp}), and many control mechanisms exist
to stabilize trajectories of the system. While many of these controllers 
are time-dependent, \citet{vlp_energy_shaping}
offer a time-independent technique to inject energy into the VLP. 
They designed a controller through a technique called \textit{energy shaping},
and proved that their control mechanism stabilizes any desired energy level set.
However, the energy injection mechanism is ad-hoc in the sense that it is not
derived from natural behaviour. 
In this chapter we will design VNHCs to stabilize energy levels of the VLP in a
time-independent manner, while maintaining the structured motion of a human on a
swing.
